Main Analyses

### 2016-02-24 Rmd/figures.Rmd
Updated results with new figure 3. Fixed small mistake in Figure 2, which was to select impact range from optimized results, not all results (very tiny difference).

```{r, eval = FALSE}
p <- data.frame(ybdc$both$params)
p[, c("Y", "C", "BD" ,"COST")] <- round(p[, c("Y", "C", "BD" ,"COST")], 2)
scens <- lapply(c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9), function(x) {
  c(1 - x, rep(x / 2, 2), 0)
})
pind <- sapply(scens, function(x) {
  x <- round(x, 2)
  which(p$Y == x[1] & p$C == x[2] & p$BD == x[3] & p$COST == x[4])
})

@@

# calculate max impacts across both crops, and figure out the impact range, 
# and what percent that is relative to the worst case
allstats <- selected_impacts(1:nrow(p), fp(p_out, ybdc$both$bcode))
minmaxstats <- allstats[, lapply(.SD, range)]
imp_range <- minmaxstats[, lapply(.SD, diff)]  # difference between best/worst
pct_of_tot <- minmaxstats[, lapply(.SD, function(x) diff(x) / max(x))]

@@

sctab <- do.call(rbind, scens) * 100
cx <- 0.7
lcols <- c("black", "red", "blue")
imp_pct[, {
  png(fp(p_figures, "weight_impact2.png"), height = 4, width = 4, 
      units = "in", res = 300)
  par(mgp = c(2, 0.75, 0), mar = c(3, 3, 1, 1))
  plot(conv_area, tot_C, type = "l", xlab = "", ylab = "", #xaxt = "n", 
       axes = FALSE, ylim = c(0, 65), xlim = c(2, 12))#, xaxs = "r", yaxs = "r")
  lines(conv_area, int_prior, col = "red")
  lines(conv_area, mu_cost, col = "blue")
  axis(1, at = seq(2, 12, 1), cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.2, mgp = c(1, 0.25, 0))
  axis(2, at = seq(0, 60, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.15, mgp = c(1, 0.25, 0))
  mtext("% land savings", side = 1, line = 1, cex = cx)
  mtext("% Carbon/Biodiv/Cost savings", side = 2, line = 1, cex = cx)
  inms <- c("tot_C", "int_prior", "mu_cost")
  for(i in 1:length(inms)) {
    text(conv_area[-1], get(inms[i])[-1], labels = sctab[-1, i + 1], 
         cex = cx * 0.8, pos = 3, offset = 0.2, col = lcols[i])
    text(conv_area[1] + 0.1, i, labels = 0, cex = cx * 0.8, pos = 3, 
         offset = i * 0.15 - 0.2, col = lcols[i])
  }
  legend("bottomleft", legend = c("Carbon", "Biodiv", "Cost"), cex = cx,
         text.col = lcols, col = lcols, bty = "n", lty = 1)
  dev.off()
}]

@@

Objective weighting of outcomes, based on range of potential impacts

>>>>

```{r, eval = FALSE}
p <- data.frame(ybdc$both$params)
pare <- ybdc$both$optitab
p[, c("Y", "C", "BD" ,"COST")] <- round(p[, c("Y", "C", "BD" ,"COST")], 2)
scens <- lapply(c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9), function(x) {
  c(1 - x, rep(x / 2, 2), 0)
})
pind <- sapply(scens, function(x) {
  x <- round(x, 2)
  which(p$Y == x[1] & p$C == x[2] & p$BD == x[3] & p$COST == x[4])
})

@@

# calculate max impacts across both crops, and figure out the impact range, 
# and what percent that is relative to the worst case
allstats <- selected_impacts(pare$ind, fp(p_out, ybdc$both$bcode))
minmaxstats <- allstats[, lapply(.SD, range)]
imp_range <- minmaxstats[, lapply(.SD, diff)]  # difference between best/worst
pct_of_tot <- minmaxstats[, lapply(.SD, function(x) diff(x) / max(x))]

@@

sctab <- do.call(rbind, scens) * 100
cx <- 0.7
lcols <- c("black", "red", "blue")
imp_pct[, {
  png(fp(p_figures, "weight_impact.png"), height = 4, width = 4, 
      units = "in", res = 300)
  par(mgp = c(2, 0.75, 0), mar = c(3, 3, 1, 1))
  plot(conv_area, tot_C, type = "l", xlab = "", ylab = "", #xaxt = "n", 
       axes = FALSE, ylim = c(0, 65), xlim = c(2, 12))#, xaxs = "r", yaxs = "r")
  lines(conv_area, int_prior, col = "red")
  lines(conv_area, mu_cost, col = "blue")
  axis(1, at = seq(2, 12, 1), cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.2, mgp = c(1, 0.25, 0))
  axis(2, at = seq(0, 60, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.15, mgp = c(1, 0.25, 0))
  mtext("% land savings", side = 1, line = 1, cex = cx)
  mtext("% Carbon/Biodiv/Cost savings", side = 2, line = 1, cex = cx)
  inms <- c("tot_C", "int_prior", "mu_cost")
  for(i in 1:length(inms)) {
    text(conv_area[-1], get(inms[i])[-1], labels = sctab[-1, i + 1], 
         cex = cx * 0.8, pos = 3, offset = 0.2, col = lcols[i])
    text(conv_area[1] + 0.1, i, labels = 0, cex = cx * 0.8, pos = 3, 
         offset = i * 0.15 - 0.2, col = lcols[i])
  }
  legend("bottomleft", legend = c("Carbon", "Biodiv", "Cost"), cex = cx,
         text.col = lcols, col = lcols, bty = "n", lty = 1)
  dev.off()
}]

@@

"Objective" subjective weighting of outcomes, based on different preferences. The examples here are intended to understand the impacts that will happen when different actors with different land use interests are willing to make some compromise, e.g. they are willing to give up 5-10% of the value of their best case cost, whereas the other parties must be willing to pay more. Do that for each of the 4, and then compare to the case where each gets equal weight.

```{r, eval = FALSE}
# use minmax stats from optimal solution set
# pare <- ybdc$both$optitab
optirange <- pare[, lapply(.SD, range), .SDcols = 1:4]
# optirange[1, lapply(.SD, function(x) x * 1.05)]

# y_comp <- sweep(as.matrix(pare)[, 1:4], MARGIN = 2, swvec, `<=`)
cvar <- "C"
compromise <- function(pare, optirange, cvar, cost1 = 1.05, cost2) {  
  sval <- optirange[1, (eval(parse(text = cvar))) * cost1]
  pare_ss <- as.matrix(pare[(eval(parse(text = cvar))) <= sval])
  vars <- names(pare)[!names(pare) %in% c(cvar, "ind")]
  swvec <- as.matrix(optirange[1, vars, with = FALSE])[1, ]
  ocosts <- sweep(pare_ss[, vars], MARGIN = 2, swvec, "/")
  # cost2 <- seq(1, 2, 0.05)
  # pare_ss[2, vars][3] / swvec[3]
  # ocosts[2, ]

  chks <- sapply(cost2, function(x) {  # x <- cost2[13]
    chkvals <- ifelse(ocosts < x, 1, 0)
    chkvec <- which(rowSums(chkvals) == 3)
    if(length(chkvec) == 1) {
      ochks <- chkvec
    } else if(length(chkvec) > 1) {
      ochks <- chkvec[which.min(rowSums(ocosts[chkvec, ]))]  # select minimum
    } else {
      ochks <- 0
    }
    ochks
  })
  # pare_ss[269, ]
  # ocosts[269, ]
  # pare_ss[269, "COST"] / optirange[1, COST]
  # optirange[1, Y] * 1.05
  c("cost" = cost2[chks > 0][1], pare_ss[chks[chks > 0][1], "ind"])
}

# indices of costs in other three variables
cost2 <- seq(1, 5, 0.05)
y_comp <- compromise(pare, optirange, cvar = "Y", cost1 = 1.05, cost2 = cost2)
c_comp <- compromise(pare, optirange, cvar = "C", cost1 = 1.05, cost2 = cost2)
bd_comp <- compromise(pare, optirange, cvar = "BD", cost1 = 1.05, cost2 = cost2)
ct_comp <- compromise(pare, optirange, cvar = "COST", cost1 = 1.05, cost2=cost2)
# pare[ind == y_comp["ind"], .(Y, C, BD, COST)] / optirange[1, ]
# pare[ind == c_comp["ind"], .(Y, C, BD, COST)] / optirange[1, ]
# pare[ind == bd_comp["ind"], .(Y, C, BD, COST)] / optirange[1, ]
# pare[ind == ct_comp["ind"], .(Y, C, BD, COST)] / optirange[1, ]

# select out those values from the results tables and grab conversion areas
parms <- round(ybdc$both$params[, 7:10], 2)
eqind <- which(apply(parms, 1, function(x) all(x == 0.25))) # iter of eq wt run
# pare[ind == eqind]

pind <- c(y_comp["ind"], c_comp["ind"], bd_comp["ind"], ct_comp["ind"], eqind)
# round(ybdc$both$params[pind, 7:10], 2)
fnames <- fp(fp(p_out, ybdc$both$bcode), 
             imp_sorter(fp(p_out, ybdc$both$bcode), inds = pind))
objsubj_r <- lapply(fnames, function(x) {  # x <- pind[[1]]
  print(x)
  DT <- cbind(fread(x), basedt[, .(x, y, convertible)])
  DTr <- dt_to_raster(DT, CRSobj)
})
names(objsubj_r) <- c("ycomp", "ccomp", "bdcomp", "ctcomp", "eqwt")

# run for subjective weights (could have pull this out also) as check
# run for subjective weights, where we want to treat everyone equally
# eq_wgts <- rep(0.25, 4)
# names(eq_wgts) <- cnames  # rename to make sure model runs properly
# tosubj <- tradeoff_mod(targ, cbetas = eq_wgts, currprodmod = g, it = "SUBJ")
# tosubj_imp <- selected_impacts2(tosubj$impacts)

# tosubj_imp <- lapply(c(1, 4, 2, 6:8, 3), function(x) tosubj_imp[[x]])

# pull out the impact tables (brief check shows they are the same values)
all_stats <- selected_impacts(unname(pind), fp(p_out, ybdc$both$bcode))
impsr <- lapply(c(2, 5, 3, 7:9, 4), function(x) all_stats[[x]])
# pare[ind == y_comp["ind"],]; pare[ind == c_comp["ind"],]; 
# pare[ind == bd_comp["ind"],]; pare[ind == ct_comp["ind"],]
# tosubj_imp

# grid for calculating overlaps
pms2a <- expand.grid(rep(list(0:1), 5))[-1, ] 
pms2b <- pms2a[which(rowSums(pms2a) == 2), ]
pms2b$cl <- c("YC", "YBD", "CBd", "YCt", "CCt", "BDCt", "YEq", "CEq", 
              "BdEq", "CtEq")

toresr <- lapply(objsubj_r, function(x) calc(x[[1:2]], sum))
tores_over_r <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests
  calc(stack(toresr[which(pms2b[x, ] == 1)]), sum)
})
names(tores_over_r) <- pms2b$cl

# calculate nearest neighbor distance between each version, using spatstat 
# nncross
# plot(zam_owin)
zam_owin <- owin(xrange = bbox(zambia)[1, ], yrange = bbox(zambia)[2, ],
                 unitname = "meter")
which1 <- function(x) x == 1  # selector function for r to xy
tores_nn <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests; x = 2
  ind <- which(pms2b[x, 1:5] == 1)  ### check col number
  rl <- toresr[ind]
  rxy <- lapply(rl, function(x) rasterToPoints(x, fun = which1))
  pps <- lapply(rxy, function(x) {
    ppp(x = x[, 1], y = x[, 2], window = zam_owin)
  })
  # reorder to find which has most points, to put that in as X
  reord <- sort(sapply(pps, function(x) x$n), decreasing = TRUE)
  ppnn <- nncross(pps[[names(reord)[1]]], pps[[names(reord)[2]]])
})
pms2b$NND <- round(sapply(tores_nn, function(x) mean(x$dist))) / 1000
# with(pms2b, plot(NND, JS))

# cols_tr <- c(rgb(1, 0, 0), rgb(1, 0.75, 0), rgb(0, 0, 1), rgb(0, 0.75, 1))
cols_tr <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0, 0.75, 1), rgb(1, 0.5, 0), 
             "gold")#rgb(1, 1, 0))
plot(1:length(cols_tr), cex = 3, pch = 20, col = cols_tr)

# layout matrix
m1 <- do.call(cbind, lapply(1:5, function(x) matrix(rep(x, 45), 6, 9)))
m2 <- matrix(rep(6, 36), 4, 9)
m3 <- do.call(cbind, lapply(7:13, function(x) matrix(rep(x, 20), 4, 5)))
f1 <- lapply(14:15, function(x) cbind(rep(x, 4), rep(x, 4)))
lmat <- rbind(m1, cbind(m2, m3, rep(14, 4)))
# lmat <- rbind(m1, m3)
# cbind(m2, m3)

# plot(1:10, ylab = ylabs[2])
# ylabs <- c("Jaccard Index", 
ylabs <- c(expression(paste("Conv. area (", 10^5, " ", km^2, ")")), 
           "Hours", "C loss (Mt)", "Priority", "Intactness/priority",
           "Intactness", expression(paste("FR converted (ha"^2, ")")))
# yscale <- c(1, 10^5, 1, 100000, 1, 1, 1, 1)
yscale <- c(10^5, 1, 100000, 1, 1, 1, 1)

# figure titles
ftits <- lapply(pind, function(x) {
  paste(sapply(1:4, function(y) {
    paste(paste(cnames[y], paste0(parms[x, y] * 100, "%")))
  }), collapse = " ")
})
leg <- c("Converted")

# yaxes <- list(seq(0, 0.8, 0.1), seq(0, 14, 2), seq(0, 2.5, 0.5), 
maxes <- sapply(c(2, 5, 3, 7:9, 4), function(j) minmaxstats[[j]][2])
mins <- sapply(c(2, 5, 3, 7:9, 4), function(j) minmaxstats[[j]][1])
ymaxes <- maxes / yscale
ymins <- mins / yscale
yaxes <- list(seq(0, 15, 3), 0:7, seq(0, 1100, 100), seq(0, 0.15, 0.05), 
              seq(0, 0.6, 0.1), seq(0, 1, 0.1), seq(0, 7000, 1000))

# bcols <- c(list(c(cols_tr[1], cols_tr[1], cols_tr[2], cols_tr[1], cols_tr[2],
pms2b$icol <- cols_tr[c(1, 1, 2, 1, 2, 3, 1, 2, 3, 4)]  # circle inner
pms2b$ocol <- cols_tr[c(2, 3, 3, 4, 4, 4, 5, 5, 5, 5)]  # circle outer

tiff(fp(p_figures, "objective-subjective_weights.tif"), height = 2.5, width = 7, 
     units = "in", res = 300)
l <- layout(mat = lmat)
# layout.show(l)

# map plots
for(i in 1:length(toresr)) { # i <- 1
  # map
#   par(mar = rep(0, 4))
#   plot(zambia, col = cols_tr[i])
  imp_plot2(toresr[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = leg, ftitle = ftits[[i]], col = cols_tr[[i]], 
            legend = TRUE, hold = TRUE, stats = FALSE, cexscale = 0.3, 
            marg = rep(0, 4), inset = c(0.1, 0.1, 0, 0))
}

# impact plots
mgp <- c(0.9, 0.25, 0)
par(mar = c(3, 3, 0, 3))
with(pms2b, {
     plot(NND, JS, col = pms2b$icol, pch = 16, cex = 0.8, 
          axes = FALSE, xlab = "", ylab = "", ylim = c(0, 0.6), 
          xlim = c(0, 25))
     points(NND, JS, col = pms2b$ocol, pch = 20, cex = 0.5)
     axis(1, at = seq(0, 25, 5), cex.axis = 0.5, las = 2, mgp = mgp, 
          tcl = -0.2)
     axis(2, at = seq(0, 0.6, 0.1), cex.axis = 0.5, las = 2, mgp = mgp, 
          tcl = -0.2)
     mtext(text = "NN Distance (km)", side = 1, line = 0.5, cex = 0.4)
     mtext(text = "Jaccard Index", side = 2, line = 1, cex = 0.4)
})
par(mar = c(3, 3, 0, 0))
mgp <- c(1.3, 0.25, 0)
for(i in 1:7) { # i <- 1
  v <- impsr[[i]] / yscale[i]
  b <- barplot(impsr[[i]] / yscale[i], las = 2,  col = cols_tr, 
               mgp = mgp, tcl = -0.2, yaxt = "n", 
               ylim = range(yaxes[[i]]), ylab = ylabs[i], cex.axis = 0.4,
               cex.lab = 0.55)
  lines(c(-1, 7), rep(ymins[i], 2), lwd = 1, col = "grey50")
  lines(c(-1, 7), rep(ymaxes[i], 2), lwd = 1)
  axis(2, at = yaxes[[i]], cex.axis = 0.5, las = 2, mgp = mgp, 
       tcl = -0.2)
}
dev.off()

# Earlier version of figure 3
